Developing a preprint culture in biology

### 2012-09-26 ms.tex
peerage of science

The review process as a whole is critically over-loaded, because the number of
active scientists increases, because the pressure to publish increases, and
because of an effect dubbed ``the tragedy of the reviewers commons'' REF.  At
the same times, rejection rates are high in most journals (REF), and when not
invited to submit a revisions, authors must start the whole process all over
again. It's thus no surprise that different initiatives emerged over the last
few years, to decrease the time spent in review. XXX et coll. (REF) called for
the recycling and reuse of peer-reviews: by attaching previous reviews, and
detailed replies, to a new submission, both the editor and the referees can
gauge the work done on the manuscript, and perhaps evaluate it with less
prejudice. In a similar way, the \emph{Peerage of Science} initiative allows
authors to seek anonymous pre-review by their peers. Some journals now accept
to publish papers which received good evaluations, effectively outsourcing the
review process. A widespread use of preprint servers can achieve the same goal
of reducing the time spent in review. By putting a manuscript for open
comments and criticisms, the authors will receive valuable feedback and can
improve the version which will be submitted. With a rich enough community of
scientists depositing preprints, and commenting on them, the process of an open
pre-review can become widespread and will overall increase the quality of
first submissions.

>>>>

The review process as a whole is critically over-loaded, because the number of
active scientists increases, because the pressure to publish increases, and
because of an effect dubbed ``the tragedy of the reviewers commons'' REF.  At
the same times, rejection rates are high in most journals (REF), and when not
invited to submit a revisions, authors must start the whole process all over
again. It's thus no surprise that different initiatives emerged over the last
few years, to decrease the time spent in review. XXX et coll. (REF) called for
the recycling and reuse of peer-reviews: by attaching previous reviews, and
detailed replies, to a new submission, both the editor and the referees can
gauge the work done on the manuscript, and perhaps evaluate it with less
prejudice. In a similar way, the \emph{Peerage of Science} initiative allows
authors to seek anonymous pre-review by their peers. Some journals now accept to
publish papers which received good evaluations, with \emph{Animal Biology}
having recently accepted first a paper reviewed entirely with the \emph{Peerage of
Science} \cite{abb12}, effectively outsourcing the review process. A widespread
use of preprint servers can achieve the same goal of reducing the time spent in
review. By putting a manuscript for open comments and criticisms, the authors
will receive valuable feedback and can improve the version which will be
submitted. With a rich enough community of scientists depositing preprints, and
commenting on them, the process of an open pre-review can become widespread and
will overall increase the quality of first submissions.
